### 2018-02-28 thesis/contents/sagit.tex
Updates from ShareLaTeX

\chapter{STUDY III: Merged Group Tractography Evaluation with Selective Automated Group Integrated Tractography}
\chaptermark{Study III}

@@

\subsection{Tractography Evaluation}
The generated visual reports were then evaluated by 5 neuroscientists in a blinded study using a set of rating criteria (See supplemental). The conjunction images were at the same time used to generate NOS scores. The NOS score quantified the conjunction image generated by overlapping tractography masks to meaningfully determine the spatial agreement independent of anatomy. The assumption was that given a conjunction image, where its voxel value s denotes a range of overlap percentages between 0\% to 100\%, and value 1 that denotes the 100\% overlap value, we formalize it as $ s\in[0,1]$, and define NOS score as: 
\begin{equation}
n^{-1} \sum_{i=0}^{n-1} \frac{\ln(v_i)}{\ln(v_0)}
\end{equation}
where $n$ was the number of bins; $v_0$ was the number of voxels where $s \textgreater 0$;  $v_i$ was the number of voxels with $ 0 \textless s \ge \frac{i}{n}$; this study used $n=10$. Examples of NOS score behaviour are available in Figure 4. 
The rater scores were then normalized to each anatomy, and the normalized rater scores were linearly regressed against the NOS scores for correlations. Linear regression of rater scores against NOS was performed using the R-statistics library [R Development Core Team, 2012].

>>>>

\chapter{STUDY III: Merged Group Tractography Evaluation with Selective Automated Group Integrated Tractography}
\chaptermark{Study III}
\label{section:study3}

@@

\subsection{Tractography Evaluation}
The generated visual reports were then evaluated by 5 neuroscientists in a blinded study using a set of rating criteria (See supplemental). The conjunction images were at the same time used to generate NOS scores. The NOS score quantified the conjunction image generated by overlapping tractography masks to meaningfully determine the spatial agreement independent of anatomy. The assumption was that given a conjunction image, where its voxel value s denotes a range of overlap percentages between 0\% to 100\%, and value 1 that denotes the 100\% overlap value, we formalize it as $ s\in[0,1]$, and define NOS score as: 
\begin{equation}
n^{-1} \sum_{i=0}^{n-1} \frac{\ln(v_i)}{\ln(v_0)}
\end{equation}
where $n$ was the number of bins; $v_0$ was the number of voxels where $s > 0$;  $v_i$ was the number of voxels with $ 0 < s \ge \frac{i}{n}$; this study used $n=10$. Examples of NOS score behaviour are available in Figure 4. 
The rater scores were then normalized to each anatomy, and the normalized rater scores were linearly regressed against the NOS scores for correlations. Linear regression of rater scores against NOS was performed using the R-statistics library [R Development Core Team, 2012].
